First, I would like to thank Prof. Anke-Susanne Müller from the Institute of Beam Physics and Technology for being my first reviewer.

I want to express my sincere appreciation for my advisor Dr. Michele Caselle for always being a great support and an excellent teacher, who always has time to explain all details, even if it concerns fundamental topics. 
His great support at all times made the successful conclusion of this thesis and my studies possible.

Prof. Serge Bielawski from Lille University I would like to thank for the collaboration and the useful feedback concerning the system.

I would also like to thank Andreas Kopmann (IPE) for his support during the writing of this thesis and the preparation of the final defence.

Michael Schleicher (IPE) I would like to thank for his useful advice and help during the design phase of the card layout.

My biggest gratitude also goes to Meghana Patil (LAS)  for her support at all times, especially during the last phase of writing and preparation of my presentation.

I would like to thank Miriam Brosi (IBPT) for giving me the possibility to see the KARA facility from inside and for prove-reading the physics part of my thesis.

I am eternally grateful to Marvin Noll for his invaluable support not only during the writing of the thesis (especially concerning LaTeX-related questions) and the preparation of the final defense, but also for his great support at any times during the whole course of my studies.

Finally, I would like to thank my parents for always supporting me in any situations at all times. I owe them my biggest appreciation for successfully completing my studies, without their support and care this would have never been possible.
